Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
adding ref for TH.
removing the section about quickcheck.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{QuickCheck}

\emph{TBD What does this have to do with the topic of the paper?}

It is enough to test properties which do not have parameters just one.
However, QuickCheck 2.3 or earlier tests
properties which do not have parameters 100 times.
More precisely, the evaluation results are memorized and they are
compared with {\tt True} 100 times.
The current maintainer of QuickCheck modified so that
properties which do not have parameters
are tested just once in its source repository.
This feature will be available in the future release.

@@

The {\tt test-framework} family is a TDD tool, 
which currently integrates HUnit, QuickCheck, SmallCheck, and Doctest.
Automatic test discovery based on prefixes of function name
and is implemented using Template Haskell.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \subsection{QuickCheck}

%% \emph{TBD What does this have to do with the topic of the paper?}
%% \emph{Acknowledgment is enough.}

%% It is enough to test properties which do not have parameters just one.
%% However, QuickCheck 2.3 or earlier tests
%% properties which do not have parameters 100 times.
%% More precisely, the evaluation results are memorized and they are
%% compared with {\tt True} 100 times.
%% The current maintainer of QuickCheck modified so that
%% properties which do not have parameters
%% are tested just once in its source repository.
%% This feature will be available in the future release.

@@

The {\tt test-framework} family is a TDD tool, 
which currently integrates HUnit, QuickCheck, SmallCheck, and Doctest.
Automatic test discovery based on prefixes of function name
and is implemented using Template Haskell~\cite{template-haskell}.
All examples and properties must be written in a single
source file.
